How predictable is extinction?

### 2018-11-28 doc/results.tex
added more to methods and results...tried at least

Because of the parameter rich ``past and vary'' model displays some modest improvements over the other models we choose this model for all further analysis.

@@

The approximate out-of-sample predictive performance for our selected model, as measured by AUC, is approximately identical to our in-sample performance (Fig. \ref{fig:fold_auc}). The quality of performance, however, is not great, with average out-of-sample AUC estimated to be just above 0.7 which is far from perfect. This result means that while we expect our model to yield consistent results when provided with new data, we do not expect that our predictions will be very accurate.
% ROC OOS estimate
\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio=true]{../results/figure/fold_auc}
  \caption{Results from our five-fold cross-validation of the time-series. Each labeled distribution of AUC values correspond to expected out-of-sample performance as estimated from that fold. Each fold represents a section of data being predicted from a model fit to all data before the start of that fold. Given that there are only five folds, performance is measured from model predictions to 4 of the folds. Folds are labeled from oldest to youngest, with the oldest fold only being predicted by a single previous fold and the youngest fold being predicted by the four previous folds.}
  \label{fig:fold_auc}
\end{figure}

When our cross-validation estimates are presented for each time interval,

>>>>

We can also compare the by-taxon in-sample performances of the four models.

Finally, we can also examine how the by-taxon in-sample performances of the four models vary over time.

@@

The approximate out-of-sample predictive performance for each of our four models, as measured by AUC, are approximately identical to each other and to our in-sample performance (Fig. \ref{fig:fold_auc}). The quality of performance, however, is not great, with average out-of-sample AUC for each of our models estimated to be about 0.77 which is far from perfect. This result means that while we expect our model to yield consistent results when provided with new data, we do not expect that our predictions will be very accurate.
% ROC OOS estimate
\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio=true]{../results/figure/fold_auc}
  \caption{Results from our five-fold cross-validation of the time-series. Each labeled distribution of AUC values correspond to expected out-of-sample performance as estimated from that fold. Each fold represents a section of data being predicted from a model fit to all data before the start of that fold. Given that there are only five folds, performance is measured from model predictions to 4 of the folds. Folds are labeled from oldest to youngest, with the oldest fold only being predicted by a single previous fold and the youngest fold being predicted by the four previous folds.}
  \label{fig:fold_auc}
\end{figure}

When our cross-validation estimates are presented for each time interval, the similarity in out-of-sample performance between the models becomes even more obvious -- while there are minor differences in the posterior estimates for individual time points, the overall structures are nearly identical.
